---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{disPack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(disPack)
```

## Simulated examples
```{r}
x = matrix(c(1, 2, 4, 3, 0, -4, 5, 0.1, 7), 3, 3)

a = rnorm(10)
b = rnorm(10)
```


### Euclidean distance
Evaluate Euclidean distance on matrix with 3 points with 3 dimensions.
```{r}
euclidean(x)
```
Add weight component and return as dist object. 
```{r}
euclidean(x, w = 0.5, output = "dist")
```
Evaluate Euclidean distance between two points with dimension 10 with weight 0.5
```{r}
euclidean(a, b, w = 0.5)
```

### Manhattan distance

Evaluate Manhattan distance on matrix with 3 points with 3 dimensions.
```{r}
manhattan(x)
```
Evaluate Manhattan distance between two points with dimension 10 with return of a dist object
```{r}
euclidean(a, b, output = "dist")
```
### Minkowski distance 
Evaluate Minkowski distance with one more parameters, p(required) and w (optional)
```{r}
minkowski(x, p = 3)
```
```{r}
minkowski(a, b, p = 0.5, w = 2)
```

### Other examples
Cosine, correlation, Chebyshev, and Chi-square distance are used in the same way as Manhattan. 
Here are some examples:

* Cosine distance
```{r}
cos_dis(x)
```
* Correlation distance
```{r}
corr_dis(x)
```
* Chebyshev distance
```{r}
chebyshev(a, b)
```
* Chi-square distance
```{r}
chiSq_dis(x)
```


## Real world case
Distance data is from: https://people.sc.fsu.edu/~jburkardt/datasets/cities/wg22_xy.txt
```{r}
data <- read.table("C:/Users/Public/Documents/disPack/dataset/wg22_xy.txt", quote="\"")
data <- as.matrix(data)
dimnames(data) <- NULL
name_list <- c("Aachen", "Augsburg", "Braunschweig", "Bremen", "Essen", "Freiburg", "Hamburg", "Hof", "Karlsruhe", "Kassel", "Kiel", "Koeln", "Mannheim", "Muenchen", "Nuernberg", "Passau", "Regensburg", "Saarbruecken", "Wuerzburg", "Bielefeld", "Luebeck","Muenster")
```

* Euclidean distance
```{r, results='hide'}
euclidean_dist = euclidean(data)
```

```{r}
row.names(euclidean_dist) <- name_list
colnames(euclidean_dist) <- name_list
```

```{r, fig.dim=c(6, 6)}
heatmap(euclidean_dist, Rowv = NA, Colv = NA, scale = "none")
```

* Cosine distance 
```{r, results='hide'}
cosine_dist = cos_dis(data)
```

```{r}
row.names(cosine_dist) <- name_list
colnames(cosine_dist) <- name_list
```


```{r, fig.dim=c(6, 6)}
heatmap(cosine_dist, Rowv = NA, Colv = NA, scale = "none")
```
